### 2018-12-20 sections/systematic_uncertainties.tex
v2.2 again fixing two last Lucia Di Ciaccio's CDS comments

Uncertainties of the data-driven multijet background in the $\Hbb$ search include
contributions from the limited size of the data sample, particularly at high jet and $b$-tag multiplicities, as 
well as from the uncertainty in the rate of fake leptons, estimated in 
different control regions (e.g.\ selected with a upper requirement on either $\met$ or $\mtw$). 
A combined normalisation uncertainty of 50\% due 
to all these effects is assigned, which is taken as correlated across jet
and $b$-tag multiplicity bins, but uncorrelated between electron and muon channels. 
No explicit shape uncertainty is assigned since the large statistical uncertainties associated with
the multijet background prediction, which are uncorrelated 
between bins in the final discriminant distribution, effectively cover all possible shape uncertainties.

>>>>

Uncertainties of the data-driven multijet background in the $\Hbb$ search include
contributions from the limited size of the data sample, particularly at high jet and $b$-tag multiplicities, as 
well as from the uncertainty in the rate of fake leptons, estimated in 
different control regions (e.g.\ selected with an upper requirement on either $\met$ or $\mtw$). 
A combined normalisation uncertainty of 50\% due 
to all these effects is assigned, which is taken as correlated across jet
and $b$-tag multiplicity bins, but uncorrelated between electron and muon channels. 
No explicit shape uncertainty is assigned since the large statistical uncertainties associated with
the multijet background prediction, which are uncorrelated 
between bins in the final discriminant distribution, effectively cover all possible shape uncertainties.
